\documentclass[a4paper,10pt]{article}
%\usepackage{cmbright}
\usepackage{newpxtext,newpxmath}
%\usepackage{times}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-10pt}\scshape\raggedright\large\bf
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItemWithoutTitle}[1]{
	\item\small{
		{\vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\multicolumn{2}{c}{\textbf{{\LARGE Guanglei Zhou}}}\\  Email: \href{mailto:}{gzhou003@e.ntu.edu.sg}&
		\href{https://linkedin.com/in/guangleizhou}{Linkedin/in/guangleizhou}\\  Mobile:~~~+86-13671877480 &
		Location: Jing'an District, Shanghai, China \\
	\end{tabular*}
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading{Nanyang Technological University}{Singapore}{Master of Science (Finance)}{Jul. 2021 -- Jan. 2023}
	\resumeSubheading{Central University of Finance \& Economics}{Beijing, China}{Bachelor of Economics (Finance)}{Sep. 2017 -- Jun. 2021}
	\resumeSubHeadingListEnd
	\vspace{3pt}
	
	
	\section{Experience}
	\resumeSubHeadingListStart
	\resumeSubheading{Shanghai International Trust}{Shanghai, China}{Associate, Structured Finance Investment Dpet.}{Feb. 2023 -- Present}
	\resumeItemListStart
	\resumeItem{Deal Sourcing}{}
	\resumeItem{Deal Execution}{Assisted in deal execution of Quasi-REITs, CMBS, Asset-backed Notes, and etc, which included CMBS of CCT Construction \& Investment, Quasi-REITs of Zhangzhou Traffic Development Group.}
	\resumeItemListEnd
	
	\resumeSubheading{Shanghai Futeng Private Equity Fund (Fortera Capital)}{Shanghai, China}{Private Equity Intern, Investment \& Research Dept.}{Jul. 2022 -- Oct. 2022}
	\resumeItemListStart
	\resumeItem{Secondaries Invests}{Participated in secondaries deals for the transfers of State-owned LP shares including the \emph{GL Capital}, Walden International, and etc. \emph{Independently} drafted IC memo, model, interviews, due diligence, NDA, TS, SPA, and etc.}
	\resumeItem{Fundrasing}{Assisted to fundraise \emph{Shanghai Yinling Jieli Xingjian Fund (L.P.)} (Secondaries, AUM: 10 BB CNY).}
	\resumeItemListEnd
	
	\resumeSubheading{JIC Technology Investment, China Jianyin Investment (JIC)}{Beijing, China}
	{Private Equity Intern, Investment Dept.}{Mar. 2022 -- Jun. 2022}
	\resumeItemListStart
	\resumeItem{Direct Invests}{Participated in growth-stage deals of AIDD unicorn investments in \emph{InSilico} (Series D+), a Series C biotech, and a Series B cancer supported biotech. Solely drafted IC memo, model, due diligence, interviews, NDA, TS, SPA, etc.}
	\resumeItem{Research}{Drafted and updated the current research report of the AIDD industry and company.}
	\resumeItemListEnd
	
	\resumeSubheading{State-Owned Double Hundred Action Development Fund, China Reform Fund Mgmt.}{Beijing, China}
	{Private Equity Intern, Investment Dept.}{Sep. 2021 -- Mar. 2022}
	\resumeItemListStart
	\resumeItem{Direct Invests}{Participated in mega (growth-stage) deals of state-owned enterprises mixed ownership reform in \emph{Haiwan Chemical}, a satellite SOE, and a UAV SOE. Drafted IC memo, valuation, interview, due diligence, TS, SPA, and etc.}
	\resumeItem{Post Management}{Updated quarterly operating data, financial data, valuation. Wrote post-mgmt memos for BoDs.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	\vspace{3pt}
	\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Chinese, Chinese (Shanghainese), English}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~MS Office (Word, Powerpoint, Excel, Outlook), \LaTeX}
	\resumeSubItem{Database}{~~~~~~~~Capital IQ, Pitchbook, Wind, Bloomberg}
	\resumeSubItem{Hard Skills}{~~~~~~Financial Modeling (DCF, LBO), Fund Operation Modeling, Due Diligence, Securitization}
	
	\resumeSubHeadingListEnd
\end{document}